Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-01 paper/changes.tex
edits to comutatinal complexity in main paper and changes regarding ssim in the changes.pdf part

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART) and Simultaneous
 Algebraic Reconstruction Technique (SART). We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART) since there
 is no prior information about the number of possible attentuation
 coefficients in the test object. Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT),
 Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  The reason for not reporting RMSE stems from the optimization
  process. The optimization routine we use transforms the
  reconstruction to a different space.  That is, in our experiments,
  we observed that for a given dataset and a set of projection
  measurements, the intensity span of histograms of reconstructed
  volumes differ across various methods and solvers. As a result, the
  RMSE values are not particularly useful.  We provide the numbers
  here to show the improvement trend but we believe it does not serve
  the interest of the community to report these.

  For the same reason, the standard setting of SSIM in matlab (for
  instance) emphasizes the intensity. We found that even when the
  quality of reconstruction is acceptable visually, the SSIM values
  were not acceptable.  We choose
  to focus on preserving the structures on our reconstructions, and
  not rely on the absolute intensity values alone. Hence, we choose
  SSIM with a higher weightage to structure-preservation. For our
  record, we have computed RMSE values as well and they are presented
  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

>>>>

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART) and Simultaneous
 Algebraic Reconstruction Technique (SART). We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART) since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT),
 Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{asfdaf}. The optimization routine we use
  transforms the reconstruction values to a different range of
  numerical values.  That is, in our experiments, we observed that for
  a given dataset and a set of projection measurements, the intensity
  span of histograms of reconstructed volumes differ considerably across various
  methods and solvers.  As a result, the RMSE values are not
  particularly useful, and may even be misleading.  We provide the RMSE numbers below to show the
  improvement trend but we believe it does not serve the interest of
  the community to report these in the main paper.

  For the same reason, the standard setting of SSIM in matlab (for
  instance) emphasizes the intensity. We found that even when the
  quality of reconstruction is acceptable visually, the SSIM values
  with the standard values were not acceptable.  We choose
  to focus on preserving the structures on our reconstructions, and
  not rely on the absolute intensity values alone. Hence, we choose
  SSIM with a higher weightage to structure-preservation.

  For the record, sample RMSE values are presented
  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse} that shows
  the superiority of method at the risk of misleading absolute numbers.

  %% Why not combine all of the values in one table?

### 2021-10-01 paper/post_tci.tex
edits to comutatinal complexity in main paper and changes regarding ssim in the changes.pdf part

Most of the
computation time in our technique is used for the generation of low quality eigen-space
by reconstructing each of the templates using TV and FDK. If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs. With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver (refer code in~\cite{codeRepo}) on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent. Here below, we describe the
time complexity of spatially-varying prior technique.  Let
\begin{itemize}
\item $N$ denote the number of voxels of test volume,
\item $L$ denote the number of templates available,
\item $M$ denote the number of pilot reconstruction algorithms used for the computation of weights map, and
\item $F$ denote the time taken for optimization.
\end{itemize}
$F$ consists of time taken for alternate minimization of Eq.~\ref{eq:spatially_varying_prior}, which in turn consists of time taken for repeated cycles of a closed-form update of $\boldsymbol{\alpha}$ (Eq.~\ref{eq:compute_alpha}) and an iterative optimization of  $\boldsymbol{x}$ (Eq.~\ref{eq:compute_x}). Speed of iterative optimization is dependent on the number of imaging views as well. Therefore, the time computational complexity of our method is sum of the following
\begin{itemize}
\item $O(NL^2+L^3)$ for creating eigenspace,
\item $O(NL)*M$ for deriving weights map, and
\item time $F$  taken for iterative minimization
\end{itemize}
where $O(.)$ is the notation for `Big O' used in complexity analysis. 

>>>>

Most of the computation time in our technique is used for the
generation of low quality eigen-space by reconstructing each of the
templates using TV and FDK. If the set of projection views for every
test is fixed a priori, a reasonable assumption,
the set of low quality reconstructions can be
produced offline and stored in order to save computational costs. With
this assumption, Table~\ref{table:compute_time} shows the computation
times for various stages of reconstruction of a 2D slice of Liver
(refer code in~\cite{codeRepo}) on MATLAB 2019a on an AMD 2920X
12-Core Processor machine with 64GB RAM. If however, new sets of
projection views for every test are to be allowed, the low quality
reconstructions can still be performed efficiently using
parallelization since these reconstructions are completely
independent. Here below, we describe the time complexity of
spatially-varying prior technique.  Let
\begin{itemize}
\item $N$ denote the number of voxels of test volume,
\item $L$ denote the number of templates available,
\item $M$ denote the number of pilot reconstruction algorithms used for the computation of weights map, and
\item $F$ denote the time taken for optimization.
  $F$ consists of time taken for alternate minimization of Eq.~\ref{eq:spatially_varying_prior}, which in turn consists of time taken for repeated cycles of a closed-form update of $\boldsymbol{\alpha}$ (Eq.~\ref{eq:compute_alpha}) and an iterative optimization of  $\boldsymbol{x}$ (Eq.~\ref{eq:compute_x}). 
\end{itemize}
We ntoe that in practice $L$ is independent of $N$ and is likely to be $O(1)$  (e.g. about 12 scans in a year for disease prognosis).  Likewise $M$ is also $O(1)$. The speed of iterative optimization is dependent on the number of imaging views, and is profoundly impacted by the actual method used.  
Therefore, the time computational complexity of our method is sum of
the following
\begin{enumerate}
\item $O(NL^2+L^3)$ for creating eigenspace, which is, in practice linear, i.e., $O(N)$
\item $O(NL)*M$ for deriving weights map, which is, in practice linear, i.e., $O(N)$
\item and the time $F$  taken for iterative minimization, which as mentioned above is not the key contribution of this paper. 
\end{enumerate}
In short, the additional burden of the key idea of this paper viz. generating weights map is linear in the number of voxels, although admittedly the burden $F$ of repated optimization drives up the cost.
